% status: 0
% chapter: TBD

\title{Amazon S3}


\author{Swarnima Sowani}
\affiliation{%
  \institution{Indiana University}
  \streetaddress{Smith Research Center}
  \city{Bloomington} 
  \state{IN} 
  \postcode{47408}
  \country{USA}}
\email{shsowani@iu.edu}

\newcommand{\GE}{\footnote{Grammar}}
\newcommand{\GVL}[1]{\footnote{#1}}
% The default list of authors is too long for headers}
\renewcommand{\shortauthors}{G. v. Laszewski}

\begin{abstract}

  \emph{GVL: THis filler sentence seems irrelevant for the paper.
    Recent increased usage of internet is causing a huge volume of
    data creation which creates a growing demand for large capacity
    storage solutions. The advancements in the cloud technologies has
    yielded new ways of storing, accessing and managing data.}

Amazon provides\GE Simple Storage Service (S3) 
which is an object storage built to store and retrieve any amount
of data from anywhere such as web sites and mobile apps and corporate
applications. Amazon S3 is the cloud storage that provides storage solution
with query in place functionality which allows user to run powerful\GVL{really} analytics
directly on your data at rest\GVL{I hope you explain in the paper what
at rest means} in S3.

\end{abstract}

\keywords{hid-sp18-420, AWS, Amazon S3, i526, Simple Storage System}

\maketitle

\section{Introduction}

Amazon S3 is\GVL{the word is is wrong here. The term S3 stands for
  ..., than highlight the three s'es with bf} a simple storage service
provided by Amazon web services (AWS) which mainly\GVL{delete} focuses
on a highly scalable, reliable, and low latency data storage
infrastructure at low costs~\cite{hid-sp18-420-amazon-S3-FAQ}. Simple
storage Service is a web service provided by Amazon that can be used
to store and retrieve data of any kind and any amount at anytime from
anywhere on the web.\GVL{somewhat duplicated to first sentence?} It
can also be used for static website hosting for different web
applications. Important feature\GE of S3 is that it is available at
any point of time and can be used to store virtually\GVL{virtually is
  bad term} any kind of data in any
format~\cite{hid-sp18-420-amazon-S3-FAQ}.

One of the important features of using S3 is that it offers a highly
durable, scalable, and secure destination for backing up and archiving
critical data~\cite{hid-sp18-420-amazon-S3}. As per AWS documentation,
``Amazon S3 is designed to deliver 99.999999999\% durability, and it
is used to store data for millions of applications used by market
leaders in every industry''~\cite{hid-sp18-420-amazon-S3}.

Amazon S3 provides versioning capability to provide\GE\GVL{duplicated
  word} even further protection for stored data. It is
easy\GVL{unsubstianted claim, and we hope you clarify in paper} to
define lifecycle rules to automatically migrate less frequently
accessed data. User\GE can store any number of objects. Total
volume\GE is unlimited\GVL{wrong} but one object size can range from 0
bytes to 5 terabytes. With AmazonS3, user\GE needs to pay only for
what the usage is. But\GVL{why but, but in comparison to what} price
vary as per the chosen region of S3.



\section{Concepts and Architecture}

Amazon S3 stores data within resources called buckets and data is
stored as an object\GVL{what is an object}. Each bucket has its own
unique name and this name is unique globally\GVL{why not just globally
  unique. What does globally mean? Globally for me or globally for all
  users?}.  This global namespace allows users to have the unique
bucket globally which helps to organize their data and identify the
user to be charged for storage and data transfers.\GVL{unclear} It
also plays an important role in access control and finally\GVL{why
  finally?} it serves as the unit of aggregation for audit reports.


One bucket can have unlimited number of objects\GVL{so it has more
  capacity that the number of atoms in the universe? I find that hard
  to believe.} but number of buckets are limited to 100 per
account. Each object consists of two parts as an opaque blob and
metadata which is nothing\GVL{term} but a user specified key value
pair and predefined metadata such as LastModified date time.


Users can access or create objects based on the access control
restrictions applied to that bucket. Amazon S3 \GVL{ has a ... this is
  limited to ...} search functionality is limited to the bucket
\GVL{sentence is now becoming unclear} and is based on the object name
only with either full name or any prefix.  Amazon does not provide
content based search functionality for S3.



\section{Key Features}

\GVL{We list some ey features of S3 next.}

\subsection{Simplicity and Flexibility} 

Amazon s3 is simple to access using web based AWS management console,
mobile app, full REST APIs and AWS SDKs for integration with Mobile
SDK, Java, PHP, Python, \.NET, Node.js, Ruby. S3 features allows users
to take data driven approach for optimization and management of data
efficiently.


\subsection{Data Durability and Reliability} 

``Amazon S3 provides durable infrastructure to store important data and is
designed for durability of 99.999999999\% of objects. Your data is redundantly
stored across multiple facilities and multiple devices in each
facility''~\cite{hid-sp18-420-amazon-S3}.

\subsection{Simple Data Transfer} 

Data transfer can be made simple using Amazon S3.\GVL{placement shoudl
  be at and and a justification for simple is needed} Amazon provides
set of tools and different options for migration of data and makes it
simple and to move large volume files from Amazon S3.\GVL{runaway
  sentence, yet with the same info as previous sentence} Using S3
transfer acceleration~\cite{hid-sp18-420-amazon-S3-dataTransfer-FAQ},
it is fast, easy and secure to transfer files over long distance. AWS
Snowball \cite{?}, AWS Snowball Edge \cite{?} and AWS Snowmobile
\cite{?} are used for large scale data transfers where transferring is
made at one fifth of the cost of high speed
internet~\cite{hid-sp18-420-amazon-S3-cloud-migration}.

\subsection{Security and Access Management} 

Amazon S3 provides multiple mechanisms to provide data security and to control
or monitor data access to user.


\begin{description}

\item [User identities.] Each user registered to Amazon’s web service
  gets an identity. These identities are linked to credit cards to
  prevent one person to create multiple fake user accounts. S3 also
  has a concept of anonymous requests when no information is
  associated about user within the request.

\item [Access control.]Access controls are given by access control
  lists (ACL). Each ACL can specify the access for up to 100
  identities. S3 supports different access controls.

\begin{description}
\item [FULLCONTROL] The owner preserves full control over the object
  with all permissions.
\item [READ] It is given to buckets or users to read the object.
\item [WRITE] It is given to buckets so that user can create objects
  in the bucket.
\item [READACL] It is given to buckets or objects by which a user can
  read the ACL and get the identity of the owner.
\item [WRITEACL] It is given to user to change the Access control
  list. It is similar to full user control since the user can assign
  any right.
\end{description}

\item [Encryption.]  Data can be securely uploaded or downloaded in S3
  using SSL encrypted endpoints. If user chooses to server side
  encryption, Amazon s3 will automatically encrypt the data on every
  write and decrypt the data on every
  read~\cite{hid-sp18-420-amazon-S3-data-encryption}.

\item [Versioning.] Amazon S3 provides versioning capability to
  preserve and restore all the versions of objects in a bucket. This
  allows the recovery for any application failure or wrong action of
  user or it is available whenever required for reference. User can
  configure life cycle
  riles~\cite{hid-sp18-420-amazon-S3-lidecycle-rule} to automatically
  manage the versioning.

\end{description}

\subsection{Storage Classes}

Amazon S3 provides different storage classes depending upon the requirement and
use.

\begin{description}

\item [Amazon S3 Standard] it is used for the storage data that is
  frequently accessed.
\item [Amazon S3 Standard Infrequent Access] It is used for storing
  data which is not used more frequently but need to be stored for
  long time.
\item [Amazon Glacier] It is used for archiving data at low cost. 

\end{description}


\subsection{Query in Place} 

This is one of the important feature\GE of Amazon which provides suit
of tools for analyzing and processing huge amount of data in the cloud
faster along with different ways to integrating existing workflows
with Amazon S3.\GVL{sentence} Using Amazon S3Select\GVL{now there is
  something new how doe this relate to other terms you introduce. I
  think you may need a glossary in a figure to deal with all the terms
  the reader is by now confused} users can scan and filter data
without retrieving storage which accelerates the performance and
reduces the cost of analytics. It can process data within an object in
storage at rest\GVL{what does this term mean}, and Amazon Athena
\cite{} and Amazon Redshift Spectrum \cite{?} enable
you to run sophisticated analytics directly on data stored in S3.

\section{Use cases}
There can be multiple ways and multiple use cases\GVL{what is the
  difference between ways and use cases} in which user\GE can use Amazon
S3 as a storage solutions. 

\begin{description}
\item [Static web content and media.] Amazon S3 is widely used for
  storing static web content and media for different
  applications. Each object in the S3 has a unique HTTP URL to access
  that object. Hence, this content can be delivered directly. Amazon
  S3 can be used as an origin store for content delivery networks like
  Amazon CloudFront \cite{?}.  Amazon S3 is suited for hosting web
  content that requires bandwidth for addressing extreme spikes in
  demand. For fast growing websites such as hosting data intensive
  content like video or photo sharing websites, Amazon S3 is the
  solution as it does not require any additional storage provisioning.
 
\item [Host Static Website.]  Amazon S3 can be used to host static
  website as it provides low cost and highly available
  solution. User\GE can store static HTML files, images, videos\GVL{is
    that not static web content?} and scripts such as java script
  easily.

\item [Computation and Analytics.]  Amazon S3 is used as a data store
  for big data analytics. It is suitable for data that requires large
  scale analysis like financial transaction analysis and multimedia
  transcoding.\GVL{where are citations for the usecases} Since Amazon
  S3 is scalable horizontally, user can access data from multiple
  computing nodes simultaneously without any constrain of single
  connection. AWS offers different services that helps user\GE to manage
  big data.

\item [Backup and Archive.]  Amazon S3 offers secure and scalable
  solution\GE to backup critical data. User can use Amazon glacier
  \cite{?} to move data from S3 for backup purpose. Amazon S3 cross
  origin replication is also available which can automatically copy\GE
  objects to S3 buckets in different regions
  asynchronously.\GVL{unclear as region is not explained}
  Lifecycle rules can be defined to migrate less frequent data to S3
  standard\GVL{what is that} infrequent access and archive to Amazon Glacier. Amazon
  also provides versioning capability for S3 data. User can create
  different versions of data and hence can keep the\GE backup with older
  version and new data will get updated version.

\end{description}

\section{Pricing}

For Amazon S3 storage, user\GE needs to pay only for the storage
used. There is no cost required for setup and no minimum fee
applicable. Amazon S3 pricing is based on the storage in the form of
per gb per month, data transfer and number of requests per month.
``For new user\GVL{but what is it for a real user. new user could trap
you. what is cost for moving data out.}, AWS free tier
provides discount which includes 5GB storage, 20000 get requests, 2000
put requests and 15 GB data transfer for
free''~\cite{hid-sp18-420-amazon-S3-pricing}. Amazon S3 provides
pricing that differs based on region.


\begin{acks}

  The author would like to thank Dr.~Gregor~von~Laszewski for his
  support and suggestions to write this paper.\GVL{I did now more than
  that}

\end{acks}

\bibliographystyle{ACM-Reference-Format}
\bibliography{report} 
